Dysregulation of Cerebral Hemoglobin Content in Malawian Children with Malaria

### 2021-07-19 figures.Rmd
adjust font sizes

  # plot variables
  geom_point(data = df_vars, aes(x = PC1*5, y = PC2*5)) +
  geom_text_repel(data = df_vars, aes(x = PC1*5, y = PC2*5, label = variable, size = 10), show.legend = FALSE) +
  geom_segment(data = df_vars, aes(x = 0, y = 0, xend = PC1*5, yend = PC2*5), arrow = arrow()) +

@@

    xlab("") +
    ylab("") +
    theme_bw() +
    theme(text = element_text(family = "Arial"),
          axis.text.x = element_text(angle = 45, hjust = 0.9),
          axis.text = element_text(size = 35),
          legend.text = element_text(size = 40),
          legend.title = element_text(size = 50),
          legend.key.size = unit(2, 'cm'),
          plot.title = element_text(size = 30)
    )

@@

  labs(y = "", x = "Time (s)") +
  ggtitle("Detrended cumulative signal") +
  theme_bw() +
  theme(text = element_text(family = "Arial"),
        axis.text = element_text(size = 20),
        axis.title = element_text(size = 25),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 20),
        title = element_text(size = 25))

>>>>

  # plot variables
  # geom_point(data = df_vars, aes(x = PC1*5, y = PC2*5)) +
  # geom_text_repel(data = df_vars, aes(x = PC1*5, y = PC2*5, label = variable, size = 10), show.legend = FALSE) +
  geom_segment(data = df_vars, aes(x = 0, y = 0, xend = PC1*5, yend = PC2*5), arrow = arrow()) +

@@

    xlab("") +
    ylab("") +
    theme_bw() +
    theme(text = element_text(family = "Arial"),
          axis.text.x = element_text(angle = 45, hjust = 1),
          axis.text = element_text(size = 35),
          legend.text = element_text(size = 40),
          legend.title = element_text(size = 50),
          legend.key.size = unit(2, 'cm'),
          plot.title = element_text(size = 30)
    )

@@

  labs(y = "", x = "Time (s)") +
  ggtitle("Detrended cumulative signal") +
  theme_bw() +
  theme(text = element_text(family = "Arial"),
        axis.text = element_text(size = 25),
        axis.title = element_text(size = 28),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 20),
        title = element_text(size = 25))
